Introducing statistics with \\texttt{intRo}

### 2014-12-09 student-paper-competition-2014/paper.Rmd
Formatting for paper

---
title: "Introducing statistics with \\texttt{intRo}"
author: "Eric Hare & Andee Kaplan"
date: "December 14, 2014"
output:
  pdf_document:
    includes:
      in_header: preamble.tex
    number_sections: yes
bibliography: refs.bib
---
\thispagestyle{empty}
\begin{abstract}
\texttt{intRo} is a modern web-based application for performing basic data analysis and statistical routines. Leveraging the power of \texttt{R} and \texttt{Shiny}, \texttt{intRo} implements common statistical functions in a powerful and extensible modular structure, while remaining simple enough for the novice statistician. This simplicity lends itself to a natural presentation in an introductory statistics course as a substitute for other commonly used statistical software packages, such as \texttt{Excel} and \texttt{JMP}. \texttt{intRo} is currently deployed at the URL \url{http://www.intro-stats.com}. Within this paper we introduce the application and explore the design decisions underlying \texttt{intRo} as well as highlight some challenges and advantages of reactive programming.
\end{abstract}

\newpage
\setcounter{page}{1}

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=0.8\textwidth]{images/ui_annotate.png}
\caption{The five elements that comprise the \texttt{intRo} application: 1) top navigation, 2) side navigation, 3) options panel, 4) results panel, and 5) code panel.}
\label{fig:ui}
\end{figure}

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=\textwidth]{images/app_creation_modules.png}
\caption{This figure depicts how the \texttt{server.R} and \texttt{ui.R} files are populated using the modular structure within \texttt{intRo}.}
\label{fig:app_creation_modules}
\end{figure}

@@

\footnotesize
```{r ui, eval=FALSE}
## Source ui
module_info <- read.table("modules/modules.txt", header = TRUE, sep=",")
sapply(file.path("modules", dir("modules")[dir("modules") != "modules.txt"], "ui.R"), source)

@@

\footnotesize
```{r server, eval=FALSE}
shinyServer(function(input, output, session) {
  ## Module info
  module_info <- read.table("modules/modules.txt", header = TRUE, sep=",")

@@

  ## Source the modules
  for (mod in modules_tosource) {
      source(mod, local = TRUE)
  }
}
```
\normalsize
In this way, we were able to have \texttt{intRo} be fully extensible, its structure and functionality dependent entirely on the modules present within the application.

>>>>

---
title: "Introducing statistics with \\texttt{intRo}"
author: "Eric Hare & Andee Kaplan"
date: "December 14, 2014"
output:
  pdf_document:
    includes:
      in_header: preamble.tex
    number_sections: yes
bibliography: refs.bib
---
\thispagestyle{empty}

\begin{abstract}
\texttt{intRo} is a modern web-based application for performing basic data analysis and statistical routines. Leveraging the power of \texttt{R} and \texttt{Shiny}, \texttt{intRo} implements common statistical functions in a powerful and extensible modular structure, while remaining simple enough for the novice statistician. This simplicity lends itself to a natural presentation in an introductory statistics course as a substitute for other commonly used statistical software packages, such as \texttt{Excel} and \texttt{JMP}. \texttt{intRo} is currently deployed at the URL \url{http://www.intro-stats.com}. Within this paper we introduce the application and explore the design decisions underlying \texttt{intRo} as well as highlight some challenges and advantages of reactive programming.
\end{abstract}

\twocolumn
\setcounter{page}{1}

@@

\begin{figure*}[ht!]
\centering
\includegraphics[width=\linewidth]{images/ui_annotate.png}
\caption{The five elements that comprise the \texttt{intRo} application: 1) top navigation, 2) side navigation, 3) options panel, 4) results panel, and 5) code panel.}
\label{fig:ui}
\end{figure*}

@@

\begin{figure*}[ht!]
\centering
\includegraphics[width=\linewidth]{images/app_creation_modules.png}
\caption{This figure depicts how the \texttt{server.R} and \texttt{ui.R} files are populated using the modular structure within \texttt{intRo}.}
\label{fig:app_creation_modules}
\end{figure*}

@@

\footnotesize
```{r ui, eval=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=25)}
## Source ui
module_info <- read.table("modules/modules.txt", header = TRUE, sep=",")
sapply(file.path("modules", dir("modules")[dir("modules") != "modules.txt"], "ui.R"), source)

@@

\footnotesize
```{r server, eval=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=25)}
shinyServer(function(input, output, session) {
  ## Module info
  module_info <- read.table("modules/modules.txt", header = TRUE, sep=",")

@@

  ## Source the modules
  for (mod in modules_tosource) {
      source(mod, local = TRUE)
  }
})
```
\normalsize
In this way, we were able to have \texttt{intRo} be fully extensible, its structure and functionality dependent entirely on the modules present within the application.
